---
title: 'Diagonal Tree Plot'
author: "Daniel Lee"
date: "9/25/2016"
output: 
  html_document:
    css: style.css
theme: lumen
highlight: pygments
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache = T)
```

The required library for this plot are **igraph**, **networkD3**, **knitr**, **data.table**, **rmarkdown** and **data.table**.

```{r 'load library', include=F}
suppressMessages(require(igraph))
suppressMessages(require(networkD3))
suppressMessages(require(knitr))
suppressMessages(require(data.table))
suppressMessages(require(rmarkdown))
```

In practical, the raw data may come in multiple format. The format that I encountered most are **2 column based (from - to)** and **multiple column based (lvl1 - lvl2 - lvln)**. In this example, I will use **multiple column format** in which each column represent one hierarchy level and the hierarchy level is ordered from left to right.

In some scenario, the same element may occur in multiple column, which is totally make sense to the specific use case. However, the diagonal tree would not work in this regard. I will highlight in the comment when the treatment is in place to cater this issue.

```{r 'create mock up  data'}
treedt <- data.table(lvl1=sample(LETTERS[1:5], 10, replace = T),
                     lvl2=sample(LETTERS[3:8], 10, replace = T),
                      lvl3=sample(LETTERS[5:15], 10, replace=T),
                      lvl4=sample(LETTERS[5:15], 10, replace=T),
                      lvl5=sample(LETTERS[16:25], 10))

kable(treedt, caption='treedt')
```




